Reassessing the Impact of Dynamic Slicing in SFL

### 2018-11-16 paper/main.tex
merge
quick pass on related work

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, reported nearly 5
years ago, no tool or client analyses use this combination
today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}

@@

Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}. \Sof{@Rui, please check if the papers are correct} The Ochiai
formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}})\]

@@

\Mar{beware, this is >>NOT<< revised! ................}\\
\Sof{@todo: review this}

\textbf{Program Slicing}: Most recently related tool is ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}. \Fix{...}

Program Slicing~\cite{Weiser:1981:PS:800078.802557} is a technique to
identify program entities (the slice)\comments{that influence the
  computation of} computationally related to a user-provided point of
interest (the slice criterion).

Similarly, dynamic slicing lacks successful cases of downstream
analyses. The WhyLine debugging assistant~\cite{whyline-website} is an
isolated case of success.

There are some approaches that utilize dynamic slicing and
spectrum-based fault localization (SFL) as fault localization methods.

@@

\Fix{...}

\subsection{Automatic Program Repair}
Automated repair techiniques have received considerable attention on
the last decade and consists of three basic steps: fault localization, patch
generation, and patch validation.  Regarding the fault localization
step, Automated Program Repair (APR) tools can be guided by statistical
fault localization techiniques to modify code which most likely
contains the fault. On this section, we will briefly describe some of
these tools.
\Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }

@@

\subsection{Dynamic Slicing and Statistical Fault Localization}

Previous works studied the impact of bringing together both dynamic
slicing and statistical fault localization applied to software
debugging.

Lei et al. proposed the use of program slices built with a
dynamic backward slicing approach to defined statistical variables
which can capture the influence of a statement execution on the output
using SFL quantification of suspiciousness to each statement\cite{lei-mao-dai-wang-2012}.

Ishii and Kutsuna proposed a fault localization method with dynamic slicing that iteratively generates failing test cases using Satisfiability Modulo Theories (SMT) solvers to get distinct slices
for each test case. The proposed method was evaluated using MATLAB/Simulink models\cite{ishii-kutsuna-2016}.

Acknowledging the dependencies problem to locate a fault in the probram, Wen\cite{wen-2012} combines the concept of critical slicing, i.e., deleting statements with no contributions to faults,
with statistical fault localization proposing a program slicing spectrum-based software fault localization model.

He et al. proposed a new method to automated fault localization with
CPSS (coverage and program structure slicing)\cite{he-zhang-liu-gao-2014}.  Based on program
execution path struture data dependency analysis, the idea is to
extract execution paths streamlined into a complete program dependence
path, reverse data dependence analysis and calculate the defect rate
with state of the art SFL techiniques (i.e., Tarantula).

\subsection{Other}

\Mar{moved to here...revise when possible...}

For example,
dependency tracking alternatives such as
JSlice~\cite{Wang:2004:UCB:998675.999455} and
JavaSlicer~\cite{hammacher-bachthesis-2008} instrument the analyzed
code~\cite{hammacher-bachthesis-2008} or modify
interpreters~\cite{Wang:2004:UCB:998675.999455} to build compact
execution traces.  Then, they process the traces to reconstruct
program states; this step recovers the dependency chains rooted in
points of interest.

ORBS~\cite{Binkley:2014:OLP:2635868.2635893} is a observation-based
slicing method independent of programming language. ORBS deletes
statements in the files of interest and checks whether the test output is
the same as the original
test~\cite{Binkley:2014:OLP:2635868.2635893}.

\Fix{revise? merge?}
Observation-Based Slicing technique, similar to Critical Slicing, is
based on deleting statements that are not relevant to the test case
failure. Although, with this technique is possible to remain the rest
of the system untouched.

>>>>

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, reported nearly 5
years ago, no tool or client analyses use this combination
today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

@@

Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}.
The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}})\]

@@

\subsection{Program Slicing}

Program Slicing is an old technique with several applications in PL
and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
implemented in different ways. Dynamic Slicing has found its main
application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
context, failing tests exist. Research in this area has mainly focused
on slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
and avoiding data and control omission
errors~\cite{Zhang:2007:TLE:1250734.1250782,
  Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
cases where tests fail because some part of the code was not executed
when it should. Dynamic fault localization techniques cannot hope to
soundly report bugs in those cases. The issue is that incorporating
static information to capture those cases can result in unacceptably
large slices, which defeats the purpose of reducing the fault search
space. It is worth noting that, conceptually, the \comb{} combination
can be used with any form of dynamic slicing. We chose an
implementation of Critical
Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.

%% ORBS~\cite{Binkley:2014:OLP:2635868.2635893,DBLP:conf/iwpc/IslamB16}
%% is a recently-proposed slicing technique that is similar to Critical
%% Slicing. It is worth noting that

\subsection{SFL}

\Mar{...Rui, please elaborate...}

\subsection{\comb{}}

Prior work has investigated the combination of dynamic slicing and
spectrum-based fault
localization~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
the methodology used in these papers vary, the overall message is that
the combination is valuable. Note that slicing alone does not provide
the guarantee of improvement to \sfl{} as statements discarded with
slicing could have been ranked lower compared to faulty
statements. This paper differs from prior work in that it uses a much
larger dataset of programs and faults and a more rigorous experimental
methodology.

\subsubsection{Applications}

\Mar{...Rui, can you revise this? I guess Luis/Davino wrote it.}

@@

\subsubsection{Automatic Program Repair}
Automated repair techiniques have received considerable attention on
the last decade and consists of three basic steps: fault localization, patch
generation, and patch validation.  Regarding the fault localization
step, Automated Program Repair (APR) tools can be guided by statistical
fault localization techiniques to modify code which most likely
contains the fault. On this section, we will briefly describe some of
these tools.
\Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }

@@
